code_analyze_unrestrained

### 2025-05-08 code_analyze_unrestrained.qmd
modified figure codes

```{r}
# across 4~14
ggplot(ds_sum) +
  geom_point(aes(x = agemo, y = unrestrained_prop)) + 
  geom_smooth(aes(x = agemo, y = unrestrained_prop), method = "lm", se = T) + 
  scale_x_continuous(name = "Age (mos)", breaks = c(4,7,11,14), limits = c(3,15)) +
  scale_y_continuous(name = "Prop(unrestrained)", breaks = seq(0, 1, .25), limits = c(0,1))
summary(lm(unrestrained_prop ~ scale(agemo), data = ds_sum))

@@

@@

## Q3-3: crawling + sitting
```{r}
ds_sum %>% 
  mutate(loc = ifelse(loc=="Walker","Crawler",loc)) %>% 
  ggplot() +
    geom_point(aes(x = agemo, y = unrestrained_prop, color = loc)) + 
    geom_smooth(aes(x = agemo, y = unrestrained_prop, color = loc), method = "lm", se = FALSE) + 
    scale_x_continuous(name = "Age (mo)", breaks = c(4,7,11,14), limits = c(3,15)) +
    scale_y_continuous(name = "Prop(unrestrained)", breaks = seq(0, 1, .25), limits = c(0,1))+
    scale_color_manual(values=loc_colors)
ggsave("figure/crawl_sit_change.png", width=6, height=4)
ggsave("figure/crawl_sit_change.eps", width=6, height=4)
summary(lm(unrestrained_prop ~ crawler + sitter + agemo, data = ds_sum))
summary(lm(unrestrained_prop ~ crawler + sitter + agemo, data = ds_sum_excl))
# here, excluding outliers or not influences a lot
```

>>>>

```{r}
# across 4~14
# ggplot(ds_sum) +
#   geom_point(aes(x = agemo, y = unrestrained_prop)) + 
#   geom_smooth(aes(x = agemo, y = unrestrained_prop), method = "lm", se = T) + 
#   scale_x_continuous(name = "Age (mos)", breaks = c(4,7,11,14), limits = c(3,15)) +
#   scale_y_continuous(name = "Prop(unrestrained)", breaks = seq(0, 1, .25), limits = c(0,1))
summary(lm(unrestrained_prop ~ scale(agemo), data = ds_sum))

@@

ggplot(ds_sum_excl) +
  geom_point(aes(x = agemo, y = unrestrained_prop)) + 
  geom_smooth(aes(x = agemo, y = unrestrained_prop, group=age_group), method = "lm", se = T) + 
  scale_x_continuous(name = "Age (mos)", breaks = c(4,7,11,14), limits = c(3,15)) +
  scale_y_continuous(name = "Prop(unrestrained)", breaks = seq(0, 1, .25), limits = c(0,1))
ggsave("figure/age_related_change_ingroup.png",width=6, height=4)
ggsave("figure/age_related_change_ingroup.eps",width=6, height=4)

@@

## Q3-3: crawling + sitting
```{r}
ds_sum %>% 
  mutate(loc = ifelse(loc=="Walker","Crawler",loc))%>%
  mutate(loc = factor(loc, 
                      levels = c("Non-Sitter","Sitter","Crawler"), 
                      labels=c("Non-Sitter","Sitter","Crawler")))%>% 
  ggplot() +
    geom_point(aes(x = agemo, y = unrestrained_prop, color = loc)) + 
    geom_smooth(aes(x = agemo, y = unrestrained_prop, color = loc), method = "lm", se = FALSE) + 
    scale_x_continuous(name = "Age (mo)", breaks = c(4,7,11,14), limits = c(3,15)) +
    scale_y_continuous(name = "Prop(unrestrained)", breaks = seq(0, 1, .25), limits = c(0,1))+
    scale_color_manual(values=loc_colors)
ggsave("figure/crawl_sit_change.png", width=6, height=4)
ggsave("figure/crawl_sit_change.eps", width=6, height=4)
summary(lm(unrestrained_prop ~ crawler + sitter + agemo, data = ds_sum))
summary(lm(unrestrained_prop ~ crawler + sitter + agemo, data = ds_sum_excl))
# here, excluding outliers or not influences a lot
```
